A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Heatmaps are cool

Our results so far suggest that \McSplit\ has broadly similar performance
trends to the constraint programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, but with much lower constant factors. Indeed,
in \cref{figure:33ved-james-versus-cp-fc-nodes-scatter} we plot the number of
recursive calls made by our algorithm on the $y$-axis versus the number made by
CP-FC on the $x$-axis, for the labelled, unconnected problem instances. We see
a close correlation: we typically do slightly less work, and sometimes do more,
but instances with more than one order of magnitude difference in search space
size are rare.

>>>>

Our results so far suggest that \McSplit\ has broadly similar performance
trends to the constraint programming, forward-checking (CP-FC) algorithm of
\citet{DBLP:conf/cp/NdiayeS11}, but with much lower constant factors. Indeed,
in \cref{figure:33ved-james-versus-cp-fc-nodes-scatter} we plot the number of
recursive calls made by our algorithm on the $y$-axis versus the number made by
CP-FC on the $x$-axis, for the labelled, unconnected problem instances. (Rather
than a simple scatter plot, we use darker colours to indicate a higher density
of points around a location.) We see a close correlation: we typically do
slightly less work, and sometimes do more, but instances with more than one
order of magnitude difference in search space size are rare.
